### 2018-04-28 Paper/intro.tex
..

The emerging field of uncertainty quantification (UQ) aims at methodologies for 
incorporating, characterizing, quantifying, propagating, and reducing the 
uncertainties associated with predictive models and simulations. For situations
involving complex physical models and compute-intensive simulations, an
efficient approach to construction of model surrogates is sought to enable UQ
in a tractable manner. Polynomial chaos expansion 
(PCE)~\cite{Xiu:2002,Ghanem:2003,Eldred:2008,Olivier:2010} and 
Gaussian Process (GP)~\cite{Rasmussen:2004} or Kriging~\cite{Stein:2012} are
among the most commonly used surrogates for scientific applications. However,
both approaches quickly become prohibitive when the set of uncertain model
inputs and parameters is large-dimensional. Specifically, in the case of a PCE,
a $d$-dimensional polynomial basis with a total order of truncation, $p$ 
requires model realizations at $(p+1)^d$ quadrature nodes to estimate the PC
coefficients using a fully-tensorized Gauss quadrature. This trend is 
illustrated below in Figure~\ref{fig:curse}.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.70\textwidth]{./Figures/quad_comp}
\caption{Number of fully-tensorized Gauss quadrature nodes ($(p+1)^d$) is plotted against PCE total order truncation, $p$ for $d$ = 2,3, and 4.}
\label{fig:curse}
\end{center}
\end{figure}

>>>>

The emerging field of uncertainty quantification (UQ) aims at methodologies for 
incorporating, characterizing, quantifying, propagating, and reducing the 
uncertainties associated with predictive models and simulations. For situations
involving complex physical models and compute-intensive simulations, an
efficient approach to construction of model surrogates is sought to enable UQ
in a tractable manner. Polynomial chaos expansion 
(PCE)~\cite{Xiu:2002,Ghanem:2003,Eldred:2008,Olivier:2010} and 
Gaussian Process (GP)~\cite{Rasmussen:2004} or Kriging~\cite{Stein:2012} are
among the most commonly used surrogates for scientific applications. However,
both approaches quickly become prohibitive when the set of uncertain model
inputs and parameters is large-dimensional. Specifically, in the case of a PCE,
a $d$-dimensional polynomial basis with a total order of truncation, $p$ 
requires model realizations at $(p+1)^d$ quadrature nodes to ecactly determine the PC
coefficients using a fully-tensorized Gauss quadrature. This trend is 
illustrated below in Figure~\ref{fig:curse}.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.70\textwidth]{./Figures/curse}
\caption{Number of multi-dimensional Gauss quadrature nodes, $(p+1)^d$ is plotted against the PCE
 total order truncation, $p$ for 2, 3, and 4 dimensional polynomial basis functions.}
\label{fig:curse}
\end{center}
\end{figure}
